Towards the near-infrared detection of brown dwarf companions: Exploring methods to detect low mass stellar companions from blended spectra \thanks{Based on observations collected at the European Organisation for Astronomical Research in the Southern Hemisphere under ESO programme 089.C-0977(A)}

### 2019-05-06 nir_companions.tex
radii radii fix

We are aware that using these radii radii has its limitations, since as stated previously, there is a degeneracy in BD mass, age, and luminosity of the companion, and in particular a combination of radius-mass and radius-age relationships~\citep{sorahana_radii_2013}. Using the PHOENIX-ACES model effective radius does not allow for any independent age constraints to be incorporated, or allow for any variability in the radii to account for uncertainties.

>>>>

We are aware that using these radii has its limitations, since as stated previously, there is a degeneracy in BD mass, age, and luminosity of the companion, and in particular a combination of radius-mass and radius-age relationships~\citep{sorahana_radii_2013}. Using the PHOENIX-ACES model effective radius does not allow for any independent age constraints to be incorporated, or allow for any variability in the radii to account for uncertainties.
